### 2011-09-14 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress

\subsection{Various Ratios in IHs}

TODO play around with ratio in Mutation, but perhaps this is not enough - in that case move this after chained IHs, and try to tweak the best one by fiddling around with ratios.

TODO summary table

TODO results

@@

@@

\subsection{Algorithms for various data characteristics}

>>>>

@@

%         NB class ChainedIHsX

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & all official test data sets \\
  Iterations        & 20 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

\begin{algorithm}
\caption{Chaining IHs}
\label{listing-experiment-chaining-ihs}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\STATE $\heu{MUT} \gets \heu{Mutation}(ratio = 0.1, limit = 1)$
\STATE $\heu{CX} \gets \heu{Crossover}(ratio = 0.1, limit = 1)$
\STATE $\heu{LB} \gets \heu{LocalBranching}(ratio = 0.1, limit = 1)$
\STATE $\heu{RR} \gets \heu{RandomRemove}(ratio = 0.1)$
\STATE $\heu{H} \gets \heu{Hungry}$
\STATE $\heu{RW} \gets \heu{RemoveWorst}$
\STATE $IHs \gets \emptyset$

\STATE $IHs \gets IHs \cup (\heu{RR}, \heu{MUT}, \heu{RR}, \heu{CX}, \heu{RW})$

\STATE $IHs \gets IHs \cup (\heu{CX}, \heu{RW}, \heu{MUT})$

\STATE $IHs \gets IHs \cup (\heu{CX}, \heu{RR}, \heu{MUT}, \heu{RW}, \heu{LB}, \heu{RW}, \heu{H})$

\FOR{$ih \in IHs$}
  \FOR{$file \in $ official test data}
    \FOR{$i = 1 \to 20$}
      \STATE $ES \gets ES \cup \{file, CH = \heu{Random}, IH = ih\}$
    \ENDFOR
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

TODO result graphs

MSH, NTH, XMA-c, XMA-p boring - finds the optimum in the first step

TODO choose the best

TODO experiment to try to improve the best
